Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
Critical caption correction, figure update pending
"union" not "overlap", also color code fixed.

% figure group results primary AD & AV contrasts
\begin{figure*}[tbp] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        ($Z$>3.4, $p$<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field of view
        (cf. \citep{hanke2014audiomovie}).
        Black: outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.
        The results of audio-description's primary $t$-contrast (blue) that
        compares geometry-related nouns spoken by the narrator to non-spatial
        nouns (\texttt{geo, groom} > all non-spatial
        categories)
        are overlaid over the movie's primary $t$-contrast (blue) that compares
        cuts to a setting depicted for the first time with cuts within a
        recurring setting
        (\texttt{vse\_new > vpe\_old}).
        }
    \label{fig:group-slices}
\end{figure*}

>>>>

% figure group results primary AD & AV contrasts
\begin{figure*}[tbp] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}

    \caption{Mixed-effects group-level (N=14) clusters ($Z$>3.4, $p$<.05
      cluster-corrected) of activity correlated with the processing of spatial
      information are displayed on top of the MNI152 T1-weighted head template,
      with the acquisition field-of-view for the audio-description study
      highlighted.
      %
      The results of the audio-description's primary $t$-contrast (blue) that
      compares geometry-related nouns spoken by the narrator to non-spatial
      nouns (\texttt{geo, groom} > all non-spatial categories) are overlaid
      on the movie's primary $t$-contrast (red) that compares cuts to a
      setting depicted for the first time with cuts within a recurring setting
      (\texttt{vse\_new > vpe\_old}).
      %
      For comparison, the union of the individual PPA localization reported
      by \cite{sengupta2016extension} are indicated as a black outline.
    }

    \label{fig:group-slices}
\end{figure*}
